Final paper detail checks and analyses

### 2021-03-09 Final_analyses_checks_notebook.Rmd
added SD for GLAD only retrospective in final analysis checks html

#### Retrospective
```{r means etc change overall retro}

vars <- dat.retro %>%
  select(gad.sum_score_base,gad.sum_score_retro,
         phq.sum_score_base,phq.sum_score_retro) %>%
  mutate(gad.retro.change = gad.sum_score_base - gad.sum_score_retro,
         phq.retro.change = phq.sum_score_base - phq.sum_score_retro) %>%
  select(gad.retro.change,
         phq.retro.change)

>>>>

#### Retrospective
GLAD only
```{r means etc change overall retro}

vars <- dat.retro %>%
  filter(Sample == "GLAD") %>%
  select(gad.sum_score_base,gad.sum_score_retro,
         phq.sum_score_base,phq.sum_score_retro) %>%
  mutate(gad.retro.change = gad.sum_score_base - gad.sum_score_retro,
         phq.retro.change = phq.sum_score_base - phq.sum_score_retro) %>%
  select(gad.retro.change,
         phq.retro.change)
